%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%-------------------GOOGLE--------------------------------------
\cventry
{Software Engineer} % Job title
{Google (Cloud Platform / Persistent Disk Data Security)} % Organization
{Kirkland, Washington} % Location
{Sept. 2023 - Aug. 2025} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
  %
    \item {
        Worked on \textbf{Persistent Disk} a reliable, high-performance block storage for virtual machine instances used by millions of GCP customers, delivering improvements in storage efficiency, cost, and security at petabyte scale.
    }
    \item {
        Contributed to a major data format optimization effort \textbf{LFF3} for \textbf{Persistent Disk} which led to a 3\% reduction in data size, resulting in significant cost savings and improved storage efficiency.
    }
    \item {
        Co-lead encryption enhancements to align with company-wide standards, improving security and adopting the latest internal cryptographic libraries.
    }
    \item {
        Leveraged existing compaction and compression logic for \textbf{Device Encryption Key} (DEK) rotation, eliminating the need for data recompression and reducing compute costs by 30\%.
    }
    \item {
        Refactored compaction workers to adopt the new \textbf{Transcoder} encoding library, enabling bulk data processing, unifying the codebase, and unlocking broader initiatives like \textbf{LFF3} and \textbf{DEK rotation}.
    }
    \item {
        Coordinated end-to-end enablement of \textbf{Transcoder} in production, catching critical bugs in staging, and ensuring smooth rollout without customer impact.
    }
  \end{cvitems}
}
%-------------------MICROSOFT--------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Microsoft (Engineering Systems RnD)} % Organization
    {Redmond, Washington} % Location
    {Feb. 2020 - Sept. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
            Co-led the design and rollout of automation for \textit{Open-Source Code} detection within \textit{Inner-Source Code}, decomposing a monolithic service into microservices. Built scalable APIs in \textbf{Azure} (\textbf{Web Jobs}, \textbf{Functions}, \textbf{Storage Containers}, \textbf{Service Bus}), achieving a 4x increase in scanning capacity and unblocking release sign-offs for flagship products such as Microsoft Windows and Office.
        }
        \item {
            Contributed to the company-wide migration from \textbf{.NET Framework} to \textbf{.NET 6.0}, collaborating with cross-functional teams to resolve compatibility challenges. Streamlined large codebases by upgrading deprecated dependencies, eliminating dead code, and consolidating duplicates, improving maintainability and performance.
        }
      \end{cvitems}
    }

%--------------------ORACLE---------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Oracle Mexico Development Center} % Organization
    {Guadalajara, Mexico} % Location
    {Jul. 2015 - Apr. 2017} % Date(s)
    {
        \begin{cvitems}
          \item {Developed web applications for Oracle Management Cloud - Enterprise Manager using \textbf{Backbone.JS},
          creating, testing, and optimizing data visualizations for Target-Analytics.}
          \item {Implemented \textit{Unit Tests} and \textit{Integration Tests} using \textbf{Selenium}
          to identify and address performance bottlenecks in the application.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Software Developer} % Job title
{Quadev (Startup)} % Organization
{Cuernavaca, Mexico} % Location
{Aug. 2013 - Jun. 2015} % Date(s)
{
    \begin{cvitems}
      \item {Collaborated with a team to build an application for \textit{SAGARPA}, a Mexican government agency. using \textbf{Java EE} and \textbf{Apache Flex}}
      \item {Led the internal effort to migrate the technology stack to \textbf{Java Spring},
      resulting in a more efficient and maintainable codebase.}
    \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
